\textbf{Policy should change to improve invited speaker diversity and reflect trainee diversity}

### 2020-02-05 submission/Table_1.Rmd
add additional suggestions & fix formatting

---
geometry: margin=1.0in
output:
  pdf_document:
    includes:
      in_header: header.tex
    keep_tex: yes
---
\begin{center}
\captionof{table}{List of suggestions and resources to increase invited speaker diversity.}
\small
\begin{tabular}{|l|l|l|}
\hline

\rowcolor{lightgray}
\textbf{Suggestion} & \textbf{Description} & \textbf{Resource} \\ \hline

Lab-invited speakers & \makecell[l]{Faculty members can request \\suggestions from trainees} & \\ \hline

Use a list & \makecell[l]{Many lists of scientists from \\under-represented and under-served \\groups are available} &  \makecell[l]{https://DiversifyMicrobiology.\\github.io/resources}\\ \hline

Create a list & \makecell[l]{Use the GitHub template \\ create a self-nomination list and \\resource for your field} & \makecell[l]{https://github.com/diversifymicrobiology/\\DiversifyMicrobiology.github.io} \\ \hline

Highlight the journey & \makecell[l]{Invite all speakers to spend \\a few moments describing their \\personal science journey} & \\ \hline

>>>>

---
geometry: margin=1.0in
output:
  pdf_document:
    includes:
      in_header: header.tex
    keep_tex: yes
---
\begin{center}
\captionof{table}{Suggestions and resources to increase invited speaker diversity.}
\small
\centering
\begin{tabular}{>{\centering\arraybackslash}m{4cm}|>{\centering\arraybackslash}m{7cm}|>{}m{5cm}}

\hline

\rowcolor{lightgray}
\textbf{Suggestion} & \textbf{Description} & \textbf{Resource} \\\hline

Trainee-invited speakers & Request suggestions from trainees, increase number of trainee-group-invited speakers & \\\hline

Use a list & Lists of scientists from under-represented and under-served groups are available in several fields &  https://DiversifyMicrobiology .github.io/resources \\\hline

Create a list & Use the GitHub template to create a self-nomination list and resource for your field & https://github.com /diversifymicrobiology /DiversifyMicrobiology.github.io \\\hline

Use resources from professional societies & Many scientific societies have a committee focused on serving individuals from under-represented and underserved backgrounds. Other societies (e.g., SACNAS) are dedicated to these issues. & SACNAS, ABRCMS, AISES, ASM Subcommittee on Minority Education \\\hline

Think outside your sub-discipline & Speakers may introduce you to a technique that is not used in your sub-discipline & \\\hline

Consider scientists outside research-focused universities & Scientists from industry, teaching-focused institutions, and non-profit orgs have different approaches to their research & \\\hline

Communicate invitation expectations & Unit leadership should explicitly communicate expectations about who is invited to speak and the desired atmosphere & \\\hline

Encourage trainees to engage & \makecell[l]{When a talk is over, ensure that \\trainees are the first to ask questions} & \\\hline

Foster an inclusive atmosphere & Consider the identities of individuals the speaker is meeting with. Ask if the speaker would like to meet a particular student group & \\\hline

Highlight the journey & Invite speakers to spend a few moments describing their personal science journey & \\\hline

### 2020-02-05 submission/Table_1.tex
add additional suggestions & fix formatting

\begin{center}
\captionof{table}{List of suggestions and resources to increase invited speaker diversity.}
\small
\begin{tabular}{|l|l|l|}
\hline

\rowcolor{lightgray}
\textbf{Suggestion} & \textbf{Description} & \textbf{Resource} \\ \hline

Lab-invited speakers & \makecell[l]{Faculty members can request \\suggestions from trainees} & \\ \hline

Use a list & \makecell[l]{Many lists of scientists from \\under-represented and under-served \\groups are available} &  \makecell[l]{https://DiversifyMicrobiology.\\github.io/resources}\\ \hline

Create a list & \makecell[l]{Use the GitHub template \\ create a self-nomination list and \\resource for your field} & \makecell[l]{https://github.com/diversifymicrobiology/\\DiversifyMicrobiology.github.io} \\ \hline

Highlight the journey & \makecell[l]{Invite all speakers to spend \\a few moments describing their \\personal science journey} & \\ \hline

>>>>

\begin{center}
\captionof{table}{List of suggestions and resources to increase invited speaker diversity.}
\small
\centering
\begin{tabular}{>{\centering\arraybackslash}m{4cm}|>{\centering\arraybackslash}m{7cm}|>{}m{5cm}}

\hline

\rowcolor{lightgray}
\textbf{Suggestion} & \textbf{Description} & \textbf{Resource} \\\hline

Trainee-invited speakers & Request suggestions from trainees, increase number of trainee-group-invited speakers & \\\hline

Use a list & Lists of scientists from under-represented and under-served groups are available in several fields &  https://DiversifyMicrobiology .github.io/resources \\\hline

Create a list & Use the GitHub template to create a self-nomination list and resource for your field & https://github.com /diversifymicrobiology /DiversifyMicrobiology.github.io \\\hline

Use resources from professional societies & Many scientific societies have a committee focused on serving individuals from under-represented and underserved backgrounds. Other societies (e.g., SACNAS) are dedicated to these issues. & SACNAS, ABRCMS, AISES, ASM Subcommittee on Minority Education \\\hline

Think outside your sub-discipline & Speakers may introduce you to a technique that is not used in your sub-discipline & \\\hline

Consider scientists outside research-focused universities & Scientists from industry, teaching-focused institutions, and non-profit orgs have different approaches to their research & \\\hline

Communicate invitation expectations & Unit leadership should explicitly communicate expectations about who is invited to speak and the desired atmosphere & \\\hline

Encourage trainees to engage & \makecell[l]{When a talk is over, ensure that \\trainees are the first to ask questions} & \\\hline

Foster an inclusive atmosphere & Consider the identities of individuals the speaker is meeting with. Ask if the speaker would like to meet a particular student group & \\\hline

Highlight the journey & Invite speakers to spend a few moments describing their personal science journey & \\\hline
